---
title: "R Tutorials"
output: 
  html_document:
    theme: spacelab
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
---
```{r setup, include=FALSE}

```

#### Leslie Huang
#### February 26, 2017

## Checking and changing data types

When importing data, it's best not to assume that variables have been imported as the correct types.

Today's example comes from <a href="https://github.com/rudeboybert/fivethirtyeight/">FiveThirtyEight</a>. 

```{r, include=FALSE}
library(devtools)
devtools::install_github("rudeboybert/fivethirtyeight")
library(fivethirtyeight)
data(package = "fivethirtyeight")
```

```{r, echo=FALSE}
head(bad_drivers)
```

To check the type of values in a column of a dataframe, use the `class` command. Note that in R strings are called character vectors:

```{r, echo=TRUE}
class(bad_drivers$state)
```

In R, floating point numbers are called `numeric`.

```{r, echo=TRUE}
class(bad_drivers$losses)
```

Integers are `integer` type.

```{r, echo=TRUE}
class(bad_drivers$perc_alcohol)
bad_drivers$perc_alcohol <- as.numeric(bad_drivers$perc_alcohol)
```

They can be coerced to `numeric`:

```{r}
class(bad_drivers$perc_alcohol)
```

And, of course, the class of the data structure itself can be checked:

```{r}
class(bad_drivers)
```
